Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2023-03-13 data_analysis.Rmd
Edits based on reviewers' comments

```{r packages, include = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
library(lme4) # to run the glmer function for the web distance (random effects)
library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
library(multcomp) # for pairwise comparisons of land cover categories
library(flextable) # making tables
```

@@

# better log-transformed
ggarrange(ggplot(sites, aes(x = TotalSub)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(TotalSub))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$TotalSub) # not normal
shapiro.test(log(sites$TotalSub)) # normal

@@

@@

predictions <- summary(emmeans(tree100m, ~Location),type = "response")
predictions

@@

```{r tree_assumptions, echo = FALSE}
test_tree <- augment(tree100m, data = sites)
resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 21, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

@@

@@

predictions <- summary(emmeans(imperv100m, ~Location),type = "response")
predictions

@@

```{r imperv_assumptions, echo = FALSE}
test_imperv <- augment(imperv100m, data = sites)
resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 21, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

@@

@@

predictions <- summary(emmeans(tdr, ~Location),type = "response")
predictions

@@

```{r tdr_assumptions, echo = FALSE}
test_tdr <- augment(tdr, data = sites)
resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

**Road disturbance is higher in the urban center** than the urban forest (z = 39.19, df = 1, 21, p < 0.001). The means and SE's are 104 ± 3.23 vehicles/day/m for the urban forest and 398 ± 5.76 vehicles/day/m for the urban center.

@@

@@

predictions <- summary(emmeans(tdh, ~Location),type = "response")
predictions

@@

```{r tdh_assumptions, echo = FALSE}
test_tdh <- augment(tdh, data = sites)
resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

**Highway disturbance is higher in the urban center** than the urban fores (z = 9.388, df = 1, 21, p < 0.001). The means and SE's are 35.6 ± 1.89 vehicles/day/m for the urban forest and 65.0 ± 2.33 vehicles/day/m for the urban center.

@@

@@

predictions <- summary(emmeans(plant, ~Location),type = "response")
predictions

@@

```{r plant_assumptions, echo = FALSE}
test_plant <- augment(plant, data = sites)
resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Plant species richness is **significantly higher in the urban forest** than the urban center (z = -7.674, df = 1, 21, p < 0.001). The means and SE's are 13.30 ± 1.153 species for the urban forest and 3.33 ± 0.527 species for the urban center.

@@

@@

predictions <- summary(emmeans(spec, ~Location),type = "response")
predictions

@@

```{r spec_assumptions, echo = FALSE}
test_spec <- augment(plant, data = sites)
resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 21, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

@@

predictions <- summary(emmeans(light, ~Location),type = "response")
predictions

@@

```{r light_assumptions, echo = FALSE}
test_light <- augment(plant, data = sites)
resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 21, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

@@

@@

predictions <- summary(emmeans(patch, ~Location),type = "response")
predictions

@@

```{r patch_assumptions, echo = FALSE}
test_patch <- augment(patch, data = sites)
resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Patch area is **significantly higher in the urban forest** than the urban center (z = -374.2, df = 1, 21, p < 0.001). The means and SE's are 46,294.7 ± 68.040 mm² for the urban forest and 653.8 ± 7.381 mm² for the urban center.

@@

@@

predictions <- summary(emmeans(road, ~Location),type = "response")
predictions

@@

```{r road_assumptions, echo = FALSE}
test_road <- augment(road, data = sites)
resid_road <- ggplot(test_road, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 21, p < 0.001). The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.

@@

@@

```{r search_location_assumptions, echo = FALSE}
# As is, Poisson
test_search <- augment(search, data = sites)
resid_search <- ggplot(test_search, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

```{r search_location_graph, echo = FALSE}
# raw data
raw <- sites %>% 
  group_by(Location) %>% 
  summarise(mean = mean(WalkDist),
            se = plotrix::std.error(WalkDist))

@@

ggarrange(raw_plot_search, 
          poisson_plot_search, 
          log_plot_search, 
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
          nrow = 1)
```

Using a Poisson distribution, we **searched significantly further at sites in the urban forest** than the urban center to reach the focal web (z = -10.1, df = 1, 20, p < 0.001).

@@

```{r search_land_stats}
search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
summary(search_land)
car::Anova(search_land, test.statistic = "LR")
comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

```{r search_land_graph}
#sites <- sites %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(search_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(search_land, ~Land),type = "response")

search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)

@@

**Search distance significantly varies** by land class (Chi = 340.32, df = 4, p < 0.001).

@@

@@

```{r webs_location_assumptions, echo = FALSE}
# As is, Poisson
test_webs <- augment(web, data = sites)
resid_webs <- ggplot(test_webs, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

```{r webs_location_graph, echo = FALSE}
# raw data
raw <- sites %>% 
  group_by(Location) %>% 
  summarise(mean = mean(NumWebs),
            se = plotrix::std.error(NumWebs))

@@

ggarrange(raw_plot_webs, 
          poisson_plot_webs, 
          log_plot_webs, 
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
          nrow = 1)
```

There were **significantly more webs at sites in the urban center** than the urban forest (z = 8.556, df = 1, 20, p < 0.001).

@@

# urban forest
global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_f)
out
info <- out[[12]]
with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

@@

>>>>

```{r packages, include = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
library(lme4) # to run the glmer function for the web distance (random effects)
library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
library(multcomp) # for pairwise comparisons of land cover categories
library(flextable) # making tables
library(MASS) # negative binomial tests
library(glmmTMB) # for proportion test
library(jpeg) # save pictures
```

@@

# better log-transformed
ggarrange(ggplot(sites, aes(x = TotalSub)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(TotalSub))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$TotalSub) # not normal
shapiro.test(log10(sites$TotalSub)) # normal

@@

tree100m.nb <- glm.nb(tree100m ~ Location, data = sites)
summary(tree100m.nb)

@@

predictions <- summary(emmeans(tree100m.nb, ~Location),type = "response")
predictions

@@

```{r tree_assumptions, echo = FALSE}
test_tree <- augment(tree100m.nb, data = sites)
resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Tree cover is **significantly higher in the urban forest** than the urban center (z = 13.77, df = 1, 21, p < 0.001). The means and SE's are 47.15 ± 3.46 % for the urban forest and 1.58 ± 0.37 % for the urban center.

@@

imperv100m.nb <- glm.nb(imperv100m ~ Location, data = sites)
summary(imperv100m.nb)

@@

predictions <- summary(emmeans(imperv100m.nb, ~Location),type = "response")
predictions

@@

```{r imperv_assumptions, echo = FALSE}
test_imperv <- augment(imperv100m.nb, data = sites)
resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Impervious cover is **significantly higher in the urban center** than the urban forest (z = -14.49, df = 1, 21, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.63 % for the urban center.

@@

tdr.nb <- glm.nb(Traffic_Dist_Road ~ Location, data = sites)
summary(tdr.nb)

@@

predictions <- summary(emmeans(tdr.nb, ~Location),type = "response")
predictions

@@

```{r tdr_assumptions, echo = FALSE}
test_tdr <- augment(tdr.nb, data = sites)
resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

**Road disturbance is higher in the urban center** than the urban forest (z = -2.87, df = 1, 21, p = 0.004). The means and SE's are 104 ± 36 vehicles/day/m for the urban forest and 398 ± 125 vehicles/day/m for the urban center.

@@

tdh.nb <- glm.nb(Traffic_Dist_Highway ~ Location, data = sites)
summary(tdh.nb)

@@

predictions <- summary(emmeans(tdh.nb, ~Location),type = "response")
predictions

@@

```{r tdh_assumptions, echo = FALSE}
test_tdh <- augment(tdh.nb, data = sites)
resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

**Highway disturbance is higher in the urban center** than the urban fores (z = -2.64, df = 1, 21, p = 0.008). The means and SE's are 35.6 ± 6.04 vehicles/day/m for the urban forest and 65.0 ± 9.82 vehicles/day/m for the urban center.

@@

plant.nb <- glm.nb(TotalSub ~ Location, data = sites)
summary(plant.nb)

predictions <- summary(emmeans(plant.nb, ~Location),type = "response")
predictions

plant_used.nb <- glm.nb(SubUsed ~ Location, data = sites)
summary(plant_used.nb)

predictions <- summary(emmeans(plant_used.nb, ~Location),type = "response")
predictions

@@

@@

```{r plant_assumptions, echo = FALSE}
test_plant <- augment(plant.nb, data = sites)
resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Plant species richness is **significantly higher in the urban forest** than the urban center (z = 6.61, df = 1, 21, p < 0.001). The means and SE's are 13.30 ± 1.56 species for the urban forest and 3.33 ± 0.58 species for the urban center.

@@

spec.nb <- glm.nb(spec_rad ~ Location, data = sites)
summary(spec.nb)

@@

predictions <- summary(emmeans(spec.nb, ~Location),type = "response")
predictions

@@

```{r spec_assumptions, echo = FALSE}
test_spec <- augment(spec.nb, data = sites)
resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = -3.079, df = 1, 21, p = 0.002). The means and SE's are 137 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

light.nb <- glm.nb(light_rad ~ Location, data = sites)
summary(light.nb)

@@

predictions <- summary(emmeans(light.nb, ~Location),type = "response")
predictions

@@

```{r light_assumptions, echo = FALSE}
test_light <- augment(light.nb, data = sites)
resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Light radiance is **significantly higher in the urban center** than the urban forest (z = -17.17, df = 1, 21, p < 0.001). The means and SE's are 5.89 ± 0.91 mcd/m² for the urban forest and 116.90 ± 9.39 mcd/m² for the urban center.

@@

patch.nb <- glm.nb(patch_area_mm ~ Location, data = sites)
summary(patch.nb)

@@

predictions <- summary(emmeans(patch.nb, ~Location),type = "response")
predictions

@@

```{r patch_assumptions, echo = FALSE}
test_patch <- augment(patch.nb, data = sites)
resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Patch area is **significantly higher in the urban forest** than the urban center (z = 13.08, df = 1, 21, p < 0.001). The means and SE's are 46,295 ± 11,128 mm² for the urban forest and 654 ± 144 mm² for the urban center.

@@

road.nb <- glm.nb(road_length_m ~ Location, data = sites)
summary(road.nb)

@@

predictions <- summary(emmeans(road.nb, ~Location),type = "response")
predictions

@@

```{r road_assumptions, echo = FALSE}
test_road <- augment(road.nb, data = sites)
resid_road <- ggplot(test_road, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

Total road length is **significantly higher in the urban center** than the urban forest (z = -2.74, df = 1, 21, p = 0.006). The means and SE's are 15.6 ± 7.54 m for the urban forest and 93.0 ± 40.60 m for the urban center.

@@

search.nb <- glm.nb(WalkDist ~ Location, data = sites)
summary(search.nb)

@@

```{r search_location_assumptions, echo = FALSE}
# As is, Poisson
test_search <- augment(search.nb, data = sites)
resid_search <- ggplot(test_search, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

```{r search_location_graph, echo = FALSE}
# negative binomial 
nd <- data.frame(Location = factor(levels(sites$Location)))
predictions <- augment(search.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")

nb_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
  xlab("Collection Location") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 1.5, y = 275, label = "N.S.", color = "black", size = 3)

# raw data
raw <- sites %>% 
  group_by(Location) %>% 
  summarise(mean = mean(WalkDist),
            se = plotrix::std.error(WalkDist))

@@

ggarrange(raw_plot_search, 
          poisson_plot_search, 
          log_plot_search, 
          nb_plot_search,
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binamial"),
          nrow = 1)
```

Using a negative binomial regression,  **search distance did not significantly differ between habitats** (z = -1.15, df = 1, 20, p = 0.251).

@@

```{r search_land_stats}
search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
summary(search_land)
car::Anova(search_land, test.statistic = "LR")
comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
summary(comp)

search_land.nb <- glm.nb(WalkDist ~ Land, data = sites)
summary(search_land.nb)
car::Anova(search_land.nb, test.statistic = "LR")
comp <- glht(search_land.nb, linfct = mcp(Land = "Tukey"))
summary(comp)
```

```{r search_land_graph}
#sites <- sites %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(search_land.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(search_land, ~Land),type = "response")

search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) #+
  #annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
  #annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  #annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  #annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  #annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)

@@

**Search distance does not significantly differ** by land class (Chi = 6.37, df = 4, p = 0.173).

@@

web.nb <- glm.nb(NumWebs ~ Location, data = sites)
summary(web.nb)

@@

```{r webs_location_assumptions, echo = FALSE}
# As is, Poisson
test_webs <- augment(web.nb, data = sites)
resid_webs <- ggplot(test_webs, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

```{r webs_location_graph, echo = FALSE}
# negative binomial
nd <- data.frame(Location = factor(levels(sites$Location)))
predictions <- augment(web.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(web, ~Location),type = "response")

nb_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
  ylab("Number of Webs") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)

# raw data
raw <- sites %>% 
  group_by(Location) %>% 
  summarise(mean = mean(NumWebs),
            se = plotrix::std.error(NumWebs))

@@

ggarrange(raw_plot_webs, 
          poisson_plot_webs, 
          log_plot_webs,
          nb_plot_webs,
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
          nrow = 1)
```

There were **significantly more webs at sites in the urban center** than the urban forest (z = 4.45, df = 1, 20, p < 0.001).

@@

# urban forest
global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_f)
out
info <- out[[11]]
with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

@@

```{r webs_predictors_stats_nb}
global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
#exp(info[4, 1])
#exp(info[4, 2])
#Traffic_Dist_Road (log_tdr)
#exp(info[3, 1])
#exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
#exp(info[2, 1])
#exp(info[2, 2])

# urban forest
global <- glm.nb(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_f)
out
info <- out[[12]]
with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
